\pkg{shorts}: An R Package for Modeling Short Sprints

### 2020-10-21 paper.Rmd
Draft preparation

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = FALSE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 600,
  out.width = "100%",
  fig.align = "center",
  fig.width = 6,
  fig.height = 6 * 0.618, # 1 / phi
  fig.show = "hold",
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  width = 70
)

>>>>

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = FALSE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 300,
  out.width = "100%",
  fig.align = "center",
  fig.width = 6,
  fig.height = 6 * 0.618, # 1 / phi
  fig.show = "hold",
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  width = 70
)
